---
title: "p8105_hw6_xx2416"
author: "Xicheng Xie"
date: "2022-11-29"
output: github_document
---

```{r setup, message=FALSE}
library(tidyverse)
library(purrr)
library(modelr)
library(mgcv)
```

# Problem 1

* Read the dataset
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())


```

* Doing the bootstrap
```{r}
weather_boots<-
weather_df %>% 
  bootstrap(n=5000) %>% 
  mutate(
    models=map(strap,~lm(tmax~tmin,data = .x)),
    results1=map(models,broom::tidy),
    results2=map(models,broom::glance))

```

* Produce estimate of log(beta^0*beta^1)
```{r}
log_beta<-
  weather_boots %>% 
  select(.id,results1) %>% 
  unnest(results1) %>% 
  select(.id,term,estimate) %>% 
  pivot_wider(names_from = "term",
              values_from = "estimate") %>% 
  rename(beta0='(Intercept)',beta1='tmin') %>% 
  mutate(log_beta=log(beta0*beta1)) 

log_beta %>%
  pull(log_beta) %>% 
  quantile(c(0.025,0.975))
  
log_beta %>% 
  ggplot(aes(x=log_beta))+
  geom_density()
```

* Produce estimate of r^2
```{r}
r_squred<-
  weather_boots %>% 
  select(.id,results2) %>% 
  unnest(results2) %>% 
  select(.id,r.squared)

r_squred %>% pull(r.squared) %>% quantile(c(0.025,0.975))

r_squred %>% 
  ggplot(aes(r.squared))+
  geom_density()
```

# Problem 2

* Read and clean the raw dataset.
```{r}
homicide_df<-
  read.csv("homicide-data.csv") %>% 
  mutate(city_state=str_c(city,state,sep=','),
         resolved=as.numeric(disposition=="Closed by arrest"),
         victim_age=as.numeric(victim_age)) %>% 
  filter(!city_state %in% c("Dallas,TX","Phoenix,AZ","Kansas City,MO","Tulsa,AL")) %>%
  filter(victim_race %in% c("White","Black")) 
```

* Fit a logistic regression for the city of Baltimore,MD
```{r}
baltimore_df<-
  homicide_df %>% 
  filter(city_state=="Baltimore,MD") %>% 
  select(resolved, victim_age, victim_race, victim_sex)

fit_logistic<-
  baltimore_df %>% 
  glm(resolved~victim_age+victim_race+victim_sex,data=., family = binomial())

fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR=exp(estimate),
         CI_lower=exp(estimate-std.error*qnorm(0.975)),
         CI_upper=exp(estimate+std.error*qnorm(0.975))) %>% 
  select(term,OR,starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Based on the table, the estimate of the adjusted OR for solving homicides comparing male victims to female victims is `0.426`, and the 95% confidence interval is from `0.325` to `0.558`, which means homicides in which the victim is male are significantly less likely to be resolved than those in which the victim is female.

* Run `glm` for each of the cities in the `homicide_df`, and extract the adjusted OR and CI for solving homicides comparing male victims to female victims.
```{r}
fit_logistic_all<-
  homicide_df %>% 
  nest(data=-city_state) %>% 
  mutate(
    models=map(data,~glm(resolved~victim_age+victim_race+victim_sex,data=.x, family = binomial())),
    results=map(models,broom::tidy)
  ) %>% 
  select(city_state,results) %>% 
  unnest(results) 

# Extract the estimate ORs and CIs for victim_sexMale 
results_victim_sexMale<-
  fit_logistic_all %>% 
  filter(term=="victim_sexMale") %>% 
  mutate(OR=exp(estimate),
         CI_lower=exp(estimate-std.error*qnorm(0.975)),
         CI_upper=exp(estimate+std.error*qnorm(0.975))) %>% 
  select(city_state,OR,starts_with("CI")) 

# Make a plot
results_victim_sexMale%>%
  mutate(city_state=fct_reorder(city_state,OR)) %>% 
  ggplot(aes(x=city_state,y=OR))+
  geom_point()+
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


